SDR enhancement by clouds

### 2024-03-21 article/article.Rmd
Commit 2024-03-21 21:13

To be able to detect the CE cases, we had establish a baseline, above which we can
characterize each data point as enhancement event, by estimating the occurring over
irradiance.  To have an estimation and a first insight on the phenomenon, we
experimented with two simpler approaches as the reference.  The Haurwitz's model
[@Haurwitz1945], which is as simple clear sky we have previous adjusted and had good
fit with our data [@Natsis2023], and the TSI at the top of the atmosphere.  For both
cases we tested using an appropriate relative threshold and/or an constant offset.
The initial results, showed that we can detect a big portion of the CE events. But it
was evident, by inspecting the daily plot of irradiance, that changes on the
atmospheric conditions introduced numerous false positive and false negative results.

Initially, we try to implement a simpler approach for the clear sky reference,
without the use of a radiation transfer model. We experimented with a

## Clear Sky Irradiance

In order to identify CE cases, we used a modeled approximation of the expected clear
sky GHI.  Because of the lack of observational data for the whole period, we used
some long term climatological data for the main factors responsible for the
attenuation of the broadband downward solar radiation in the atmosphere, which are
mainly the aerosols and the water vapors. Fortunately, our site participates in the
Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998], as we operate a Cimel
photometer since 2003, collocated with the CM-21 pyranometer.  The mean monthly
aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
with the equivalent water column height in the atmosphere.  The simulation of the
clear sky radiation was performed by the well established radiation transfer model
Libradtran [@Emde2016], a similar modeling approach, was also used by @Vamvakas2020.

@@

@@

## Thresholds investigation

@@

## Criteria for cloud enhancement identification

Reasoning for the  final selection...........

Many have used models or some statistical method to determine then CE thresholds.

....... cite ...... Descriptions

We used as reference a modeled clear sky approximation,

@@

\begin{equation}
\text{CE} : \begin{cases}
 \text{GHI}_\text{i} > `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\text{GHI}_\text{i} > \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4b}
\end{equation}
where: $\theta$ solar zenith angle.

@@

Include Example of days plot? Appendix?

@@

## Other method used and rejected

-   some other criteria were tested

>>>>

To be able to detect the CE cases, we had establish a baseline, above which we can
characterize each data point as enhancement event, by estimating the occurring over
irradiance.  To have an estimation and a first insight on the phenomenon, we
experimented with two simple approaches as reference.  The Haurwitz's model
[@Haurwitz1945], which is as simple clear sky we have previous adjusted and had good
fit with our data [@Natsis2023], and the TSI at the top of the atmosphere.  For both
cases we tested using an appropriate relative threshold and/or an constant offset.
The initial results, showed that we can detect a big portion of the CE events. But it
was evident, by inspecting the daily plot of irradiance, that changes on the
atmospheric conditions introduced numerous false positive and false negative
results.  To produce a more accurate reference, we had to take into account more
factors that effect the clear sky radiation and used a radiation transfer model.

## Modeled clear Sky Irradiance

We approximated the expected clear sky GHI by using a model.  Because of the lack of
observational data for the whole period, we used some long term climatological data
for the main factors responsible for the attenuation of the broadband downward solar
radiation in the atmosphere. Which are mainly the aerosols and the water vapors.
Fortunately, our site participates in the Aerosol Robotic Network (AERONET)
[@Giles2019; @Buis1998], as we operate a Cimel photometer since 2003, collocated with
the CM-21 pyranometer.  The mean monthly aerosol optical depth (AOD) on different
wavelengths is provided by AERONET, along with the equivalent water column height in
the atmosphere.  The simulation of the clear sky radiation was performed by the well
established radiation transfer model Libradtran [@Emde2016], a similar
approach, was also used by @Vamvakas2020.

@@

## CE Criteria investigation

@@

<!---
Many have used models or some statistical method to determine then CE thresholds.
-->

@@

@@

\begin{equation}
\text{CE} : \begin{cases}
 \text{GHI}_\text{i} > `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\text{GHI}_\text{i} > \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4}
\end{equation}
where: $\theta$ solar zenith angle.

@@

- Include Example of days plot? Appendix?

@@

### 2024-03-21 article/article.tex
Commit 2024-03-21 21:13

To be able to detect the CE cases, we had establish a baseline, above which we can
characterize each data point as enhancement event, by estimating the occurring over
irradiance. To have an estimation and a first insight on the phenomenon, we
experimented with two simpler approaches as the reference. The Haurwitz's model
(Haurwitz 1945), which is as simple clear sky we have previous adjusted and had good
fit with our data (Natsis, Bais, and Meleti 2023), and the TSI at the top of the atmosphere. For both
cases we tested using an appropriate relative threshold and/or an constant offset.
The initial results, showed that we can detect a big portion of the CE events. But it
was evident, by inspecting the daily plot of irradiance, that changes on the
atmospheric conditions introduced numerous false positive and false negative results.

Initially, we try to implement a simpler approach for the clear sky reference,
without the use of a radiation transfer model. We experimented with a

\hypertarget{clear-sky-irradiance}{%
\subsection{Clear Sky Irradiance}\label{clear-sky-irradiance}}

In order to identify CE cases, we used a modeled approximation of the expected clear
sky GHI. Because of the lack of observational data for the whole period, we used
some long term climatological data for the main factors responsible for the
attenuation of the broadband downward solar radiation in the atmosphere, which are
mainly the aerosols and the water vapors. Fortunately, our site participates in the
Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998), as we operate a Cimel
photometer since 2003, collocated with the CM-21 pyranometer. The mean monthly
aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
with the equivalent water column height in the atmosphere. The simulation of the
clear sky radiation was performed by the well established radiation transfer model
Libradtran (Emde et al. 2016), a similar modeling approach, was also used by Vamvakas, Salamalikis, and Kazantzidis (2020).

@@

@@

\hypertarget{thresholds-investigation}{%
\subsection{Thresholds investigation}\label{thresholds-investigation}}

@@

\hypertarget{criteria-for-cloud-enhancement-identification}{%
\subsection{Criteria for cloud enhancement identification}\label{criteria-for-cloud-enhancement-identification}}

Reasoning for the final selection\ldots\ldots\ldots..

Many have used models or some statistical method to determine then CE thresholds.

\ldots\ldots. cite \ldots\ldots{} Descriptions

We used as reference a modeled clear sky approximation,

@@

\begin{equation}
\text{CE} : \begin{cases}
 \text{GHI}_\text{i} > 1.05 \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq 60^\circ$}\\
\text{GHI}_\text{i} > \left ({ 1.18 + \frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ 78^\circ > \theta > 60^\circ$}\\
\text{Excluded measurements}, & \theta > 78^\circ
\end{cases}\label{eq:CE4b}
\end{equation}
where: \(\theta\) solar zenith angle.

@@

Include Example of days plot? Appendix?

@@

\hypertarget{other-method-used-and-rejected}{%
\subsection{Other method used and rejected}\label{other-method-used-and-rejected}}

\begin{itemize}
\tightlist
\item
  some other criteria were tested
\end{itemize}

>>>>

To be able to detect the CE cases, we had establish a baseline, above which we can
characterize each data point as enhancement event, by estimating the occurring over
irradiance. To have an estimation and a first insight on the phenomenon, we
experimented with two simple approaches as reference. The Haurwitz's model
(Haurwitz 1945), which is as simple clear sky we have previous adjusted and had good
fit with our data (Natsis, Bais, and Meleti 2023), and the TSI at the top of the atmosphere. For both
cases we tested using an appropriate relative threshold and/or an constant offset.
The initial results, showed that we can detect a big portion of the CE events. But it
was evident, by inspecting the daily plot of irradiance, that changes on the
atmospheric conditions introduced numerous false positive and false negative
results. To produce a more accurate reference, we had to take into account more
factors that effect the clear sky radiation and used a radiation transfer model.

\hypertarget{modeled-clear-sky-irradiance}{%
\subsection{Modeled clear Sky Irradiance}\label{modeled-clear-sky-irradiance}}

We approximated the expected clear sky GHI by using a model. Because of the lack of
observational data for the whole period, we used some long term climatological data
for the main factors responsible for the attenuation of the broadband downward solar
radiation in the atmosphere. Which are mainly the aerosols and the water vapors.
Fortunately, our site participates in the Aerosol Robotic Network (AERONET)
(Giles et al. 2019; Buis et al. 1998), as we operate a Cimel photometer since 2003, collocated with
the CM-21 pyranometer. The mean monthly aerosol optical depth (AOD) on different
wavelengths is provided by AERONET, along with the equivalent water column height in
the atmosphere. The simulation of the clear sky radiation was performed by the well
established radiation transfer model Libradtran (Emde et al. 2016), a similar
approach, was also used by Vamvakas, Salamalikis, and Kazantzidis (2020).

@@

\hypertarget{ce-criteria-investigation}{%
\subsection{CE Criteria investigation}\label{ce-criteria-investigation}}

@@

@@

@@

\begin{equation}
\text{CE} : \begin{cases}
 \text{GHI}_\text{i} > 1.05 \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq 60^\circ$}\\
\text{GHI}_\text{i} > \left ({ 1.18 + \frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ 78^\circ > \theta > 60^\circ$}\\
\text{Excluded measurements}, & \theta > 78^\circ
\end{cases}\label{eq:CE4}
\end{equation}
where: \(\theta\) solar zenith angle.

@@

\begin{itemize}
\tightlist
\item
  Include Example of days plot? Appendix?
\end{itemize}

@@
